% !TEX TS-program = lualatex

\AtBeginDocument{\hypersetup{pdfborder = 0 1 1, linkcolor=blue,colorlinks=true}}
\documentclass[10pt,a4paper,dvipsnames]{moderncv}
\usepackage[10pt]{extsizes}
\moderncvtheme[green]{classic}
\AtBeginDocument{\recomputelengths}
\usepackage[utf8]{inputenc}
\usepackage[top=1.1cm, bottom=1.1cm, left=1.8cm, right=1.8cm]{geometry}
\setlength{\hintscolumnwidth}{2cm}

\RequirePackage{filecontents}
\usepackage[backend=biber,maxbibnames=99,giveninits=true,doi=false,sorting=custom,defernumbers=true]{biblatex}

% Make titles clickable rather than showing urls
\ExecuteBibliographyOptions{url=false}
\newbibmacro{string+url}[1]{%
  \iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}
\DeclareFieldFormat{title}{\usebibmacro{string+url}{\mkbibemph{#1}}}
\DeclareFieldFormat[article]{title}{\usebibmacro{string+url}{\mkbibquote{#1}}}
\DeclareFieldFormat[unpublished]{title}{\usebibmacro{string+url}{\mkbibquote{#1}}}

\DeclareSortingTemplate{custom}{
  \sort{
    \field{presort}
    \literal{9999}
  }
  \sort[final]{
    \field{sortkey}
  }
  \sort[direction=descending]{
    \field{year}
    \literal{9999}
  }
  \sort[direction=descending]{
\field[padside=left,padwidth=2,padchar=0]{month}
    \literal{00}
  }
}

\firstname{Lucas}
\familyname{Gautheron}
\title{Computational Models of Human \& Social Behavior}              
% \address{242 Rue de Tolbiac}{75013 Paris}    
\email{lucas.gautheron@gmail.com}                      
\homepage{lucasgautheron.github.io}
\mobile{+33 6 79 23 86 47} 
\extrainfo{29/01/1995}
% \photo[70pt][0.5pt]{photo.png}

\usepackage{lastpage}

\rfoot{\vspace{-2em}\textcolor{gray}{\textit{\small{\thepage/\pageref{LastPage}}}}}

\def\makenamesetup{%
  \def\bibnamedelima{~}%
  \def\bibnamedelimb{ }%
  \def\bibnamedelimc{ }%
  \def\bibnamedelimd{ }%
  \def\bibnamedelimi{ }%
  \def\bibinitperiod{.}%
  \def\bibinitdelim{~}%
  \def\bibinithyphendelim{.-}}    
\newcommand*{\makename}[2]{\begingroup\makenamesetup\xdef#1{#2}\endgroup}

\newcommand*{\boldname}[3]{%
  \def\lastname{#1}%
  \def\firstname{#2}%
  \def\firstinit{#3}}
\boldname{}{}{}

% Patch new definitions
\renewcommand{\mkbibnamegiven}[1]{%
  \ifboolexpr{ ( test {\ifdefequal{\firstname}{\namepartgiven}} or test {\ifdefequal{\firstinit}{\namepartgiven}} ) and test {\ifdefequal{\lastname}{\namepartfamily}} }
  {\mkbibbold{#1}}{#1}%
}

\renewcommand{\mkbibnamefamily}[1]{%
  \ifboolexpr{ ( test {\ifdefequal{\firstname}{\namepartgiven}} or test {\ifdefequal{\firstinit}{\namepartgiven}} ) and test {\ifdefequal{\lastname}{\namepartfamily}} }
  {\mkbibbold{#1}}{#1}%
}

\addbibresource{publications.bib}
\addbibresource{talks.bib}

\AtEveryBibitem{\clearfield{tags}}

\boldname{Gautheron}{Lucas}{L.}

\begin{document}
\definecolor{DarkGreen}{RGB}{1,125,32}
\hypersetup{
colorlinks=true,
linkcolor=DarkGreen,
urlcolor=DarkGreen,
,citecolor=Green
,citebordercolor=Green
,urlbordercolor=Green
}

\definecolor{moderncvgreen}{rgb}{0.35,0.70,0.30}


\maketitle

\textbf{\textcolor{moderncvgreen}{Areas of Specialization} \ collective intelligence, computational modelling}

\section{Education}
\cventry{\textbf{2022-2025}}{Ph.D. candidate, Computational Sociology}{Interdisciplinary Centre for Science and Technology Studies, Wuppertal}{Germany}{}{``Social dilemmas in high-energy physics: a computational approach''. Supervisors: Thomas Heinze \& Radin Dardashti. $3^{1/2}$ years contract.}
\cventry{2021-2022}{M.A., History and Philosophy of Science}{Université Paris-Cité}{}{[Class rank: 1st]}{Thesis : ``Too beautiful to be false, or too beautiful to be true? Searching supersymmetry at the \textit{Large Hadron Collider}''. Supervisors: Olivier Darrigol \& Elisa Omodei.} 
\cventry{2014-2018}{Master 1, Theoretical and Experimental Physics}{Ecole Normale Supérieure de Cachan (Paris-Saclay)}{}{}{Full scholarship \& civil-servant status.}
\cventry{2012-2014}{PCSI/PC*}{Lycée Berthollet}{Annecy}{}{Mathematics, physics and chemistry. Preparation for the competitive entrance exams of the Écoles Normales Supérieures (research oriented top higher education institutions).}
% \cventry{2009\\2012}{Baccalauréat S option SI}{Lycée Louis Lachenal}{Argonay (74)}{}{}

\section{Research}

\cventry{\textbf{Mar~2023\\(on-going)}}{Research Assistant \small{(linguistics, part time)}}{Laboratoire de Sciences Cognitives et Psycholinguistique (LSCP - DEC - École Normale Supérieure)}{}{Paris}{Investigating correlations between speech heard and produced by young infants.}
\cventry{Feb~2023\\Aug~2023}{Visiting PhD student}{Medialab, Sciences Po Paris}{}{}{}
\cventry{Sep 2020\\Nov~2021}{Engineer (linguistics)}{Laboratoire de Sciences Cognitives et Psycholinguistique (LSCP - DEC - École Normale Supérieure)}{}{Paris}{
Study of language acquisition across cultures through naturalistic long-form audio recordings.
%Supervised by Alejandrina Cristia.
% \begin{itemize}%
% \item Creation of a python package for the management, storage and analysis of large datasets ($\mathcal{O}(10^4)$ hours of audio)
% \item Signal processing on long-form audio
% \item Statistical analysis (bayesian inference)
% \item CNRS Training "Basics of Machine Learning and Deep Learning" (28h)
% \end{itemize}
}

\cventry{Oct 2016\\Jan~2017}{Research Internship (astrophysics)}{Laboratoire Univers et Théories (LUTH - INSU - CNRS)}{}{Paris Meudon}{
Influence of the nuclei distribution on weak interactions' rates in core-collapse supernovae.  %Supervised by Micaela Oertel. 
% \begin{itemize}%
% \item Implementation of electron capture rates and neutrino scattering cross-sections calculations in a core-collapse supernova simulation code (Fortran, C++).
% \end{itemize}
}

\cventry{May~2016\\Jul~2016}{Research Internship (particle physics)}{Laboratoire de Physique Nucléaire et des Hautes Énergies (LPNHE - IN2P3 - CNRS)}{}{Paris}{
Diphoton analysis and phenomenology for the ATLAS experiment. %Supervised by Lydia Roos. [signal modeling \& parametrization, effective field theories]
% \begin{itemize}%
% \item New parameterization of the diphoton invariant mass distribution for a spin-2 decaying particle signal (Pythia, ROOT, RooFit, C++, Python, FeynRules, CalcHEP)
% \item NLO corrections for the spin-2 signal (MadGraph5\_aMC\_atNLO)
% \item Signal-background interferences
% \end{itemize}
}

\cventry{Oct~2015\\Jan~2016}{Research Internship (astrophysics)}{Laboratoire d'Annecy-Le-Vieux de Physique Théorique (LAPth - IN2P3 - CNRS)}{}{Annecy-Le-Vieux}{
History of modern cosmology \& science communication (\href{https://cosmology.education/}{website})
%Supervised par Richard Taillet.
% \begin{itemize}%
% \item Creation of an Internet website for students about the history of modern cosmology (\href{http://cosmology.education/}{http://cosmology.education/})
% \item Development of several simulations in C++ to illustrate the website.
% \end{itemize}
}

\cventry{May~2015\\Jul~2015}{Research Internship (particle physics)}{Laboratoire d'Annecy-Le-Vieux des Particules (LAPP - IN2P3 - CNRS)}{}{Annecy-Le-Vieux}{
Particle physics for the ATLAS experiment.
%Supervised by Stéphane Jézéquel.
% \begin{itemize}%
% \item Diphoton events analysis and local/global significance calculations with ROOT.
% \item Analysis of the performance of a new tracker prototype for HL-LHC, using MC simulations
% \item Development of a simulation to assess the impact of thermal radiation over the temperature of parts of the tracker, as part of the design of a cooling system upgrade
% \item Development of a simulation to calculate the intersections of charged particles with the sensors of a tracker prototype
% \end{itemize}
}

\nocite{*} % <==========================================================

\defbibfilter{contributed}{%
    keyword=contributedtalks or keyword=conferenceproceedings
}
\newrefcontext[labelprefix=A]
\printbibliography[title={Preprints},keyword=preprints, resetnumbers=false]
\printbibliography[title={Peer-Reviewed Publications},keyword=publications, resetnumbers=false]
\newrefcontext[labelprefix=T]
\printbibliography[title={Invited Talks},keyword=invitedtalks,resetnumbers=true]
\printbibliography[title={Contributed Talks},filter=contributed, resetnumbers=false]
\newrefcontext[labelprefix=P]
\printbibliography[title={Poster presentations},keyword=posters, resetnumbers=true]

\section{Tutorials}

\begin{itemize}
    \item Tutorial for language acquisition scientists (``LongFoRMer: A software for managing and exploiting longform recordings and their annotations''), UCLA, Department of Linguistics. June 17th 2024.

\end{itemize}

% \printbibliography[title={Seminar Talks},keyword=seminartalks]

\section{Workshops and summer schools}

\cventry{2024}{Santa Fe Institute Graduate Workshop in Computational Social Science Modeling and Complexity}{}{}{Santa Fe, New Mexico}{}
\cventry{2023}{Summer school ``Collaboration and Interdisciplinarity in Science and Technology''}{}{Interdisciplinary Summer School Series in Higher Education Research and Science Studies}{Wuppertal, Germany}{}
\cventry{2022}{Spring school ``The History, Philosophy and Sociology of Large Scale Experiments''}{4th International Spring School of the Epistemology of the Large Hadron Collider}{}{Wuppertal, Germany}{}

\section{Grants}

\cventry{2023}{G-Research}{Grants for PhD students and postdocs in quantitative fields; \textsterling1\,000}{}{}{}

\section{Journalism}

%\cventry{Novembre 2020 à Aujourd'hui}{Pigiste}{Le Média}{}{Montreuil}{Recensions d'ouvrages.}

\cventry{Dec~2019\\Nov~2020}{President \& Publication Director}{Société de Production Le Média}{}{Montreuil}{Head of a production company with 12+ full-time workers.
%Marketing procedures optimization, development of revenue forecasting models and audience data analysis.
}

\cventry{Sep~2018\\Sep~2020}{Journalist}{Le Média}{}{Montreuil}{ \href{https://www.lemediatv.fr/auteurs/lucas-gautheron-9DAnWoo5Tlav1trWgg_Qlw/articles}{Data journalism and book reviews, text \& video} (articles cited in research papers and books, and in \href{https://www.anticor.org/2019/09/10/adp-depot-dune-reclamation-au-conseil-constitutionnel-pour-briser-le-silence-autour-du-rip/}{an appeal to the French constitutional court}).
}

\newrefcontext[labelprefix=M]
\printbibliography[title={Selected press articles},keyword=press,resetnumbers=true]

\section{Programming}

\cventry{Jul~2013}{Back-end developer}{Électricité réseau Distribution de France (ErDF)}{Annecy}{}{%
Automated retrieval of large amounts of data from other company-wide applications.}
\cventry{2011\\2014}{Volunteer}{AssaultCube}{}{}{Development of a C++ 3D video game as part of an international team of volunteers.}

\section{Skills \& interests}

\cvitem{Programming}{Python (expert), and C, C++, Fortran \& Arduino (proficient); Stan, PyTorch; Pandas, SQL, HDF; PHP, HTML, JS}
\cvitem{Languages}{French (native), English (fluent/C2); Spanish (beginner)}
\cvitem{Interests}{Energy transition; climate change and the polycrisis; microcontroller programming}


\end{document}